\href{https://github.com/uds-datalab/PDBF}{PDBF} Documentation

### 2015-09-08 pdbf-doc.tex
updated documentation

@@

\noindent PDBF toolkit is written in Java and LaTeX and can be used to compile documents on Windows, Mac and Linux. PDBF documents are also platform independent and run on any desktop OS (Windows, Linux, Mac) with a browser/PDF viewer.\\

\noindent A \href{https://infosys.uni-saarland.de/publications/p1972-dittrich.html}{demo paper} of our tool is appearing at \href{http://www.vldb.org/2015/}{VLDB 2015}.

>>>>

\section{Bugs, Suggestions, Feature requests}
If you encounter bugs, have suggestions or have a feature request, then please go to the issue page open a new issue if necessary and explain your concern. You can also write us an email (ichbinkeinreh at t-online.de or jens.dittrich at cs.uni-saarland.de).

@@

\noindent PDBF toolkit is written in Java and LaTeX and can be used to compile documents on Windows, Mac, and Linux. PDBF documents are also platform independent and run on any desktop OS (Windows, Linux, Mac) with a browser/PDF viewer.\\

\noindent A \href{https://infosys.uni-saarland.de/publications/p1972-dittrich.html}{demo paper} of our tool appeared at \href{http://www.vldb.org/2015/}{VLDB 2015}.
